Incremental tactics

### 2012-05-10 doc/papers/LFMTP2012/paper.tex
paper

@@

@@

  \begin{mathpar}
    \infer{
      \jm\mr\Gamma M A \mmr {M'}
      \and
      \jcc\mmr\Gamma{\gsubst T {\msubst x M}} S {A_2}\mmmr F
    }{
      \jcc\mr\Gamma{\lam x T}{\spinecons M S}{(\prd x {A_1} {A_2})}
      \mmmr F
    }

    \infer{
      \jcr\mr\Gamma U \mmr F
      \and
      \jm\mmr\Gamma F {\app {\cst a} S} \mmmr {F'}
    }{
      \jcc\mr\Gamma U \spinenil {\app {\cst a} S} \mmmr {F'}
    }
  \end{mathpar}

>>>>

When writing critical software, high assurance against bugs is an
absolute necessity. To certify the absence of bugs in a large body of
code given its specification, human reviewing is one option, but
certainly a failible one. Formal, mathematical proof that our program
respects a certain \emph{dependability claim} gives us the assurance
that ``its trustworthyness [\ldots] would presumably last for eternity
\cite{shao2010certified}''.

Certifying

\cite{miller2011proposal}

@@

    % Defined
    \infer{
      \jh\mr\Gamma H A {\anndefined T}
      \and
      \jl\mr\Gamma A S {\mmr} {S'} {A'}
      \and
      \jcc\mr\Gamma A T S \mmmr F
      \and
      \jm\mmmr\Gamma F {A'} {\repo {R'''} } {F'}
    }{
      \jf\mr\Gamma {\app H S} {\repo{R'''}} {F'} {A'}
    }

@@

  \begin{mathpar}
    \infer{
      \jm\mr\Gamma M {A_1} \mmr {M'}
      \and
      \jcc\mmr\Gamma{\gsubst {A_2} {\msubst x {M'}}}{\gsubst T {\msubst x {M'}}} S \mmmr F
    }{
      \jcc\mr\Gamma{\prd x {A_1} {A_2}}{\lam x T}{\spinecons M S}
      \mmmr F
    }

    \infer{
      \jcr\mr\Gamma U \mmr F
      \and
      \jm\mmr\Gamma F {\app {\cst a} S} \mmmr {F'}
    }{
      \jcc\mr\Gamma {\app {\cst a} S} U \spinenil \mmmr {F'}
    }
  \end{mathpar}
